Analysing the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Correct graph and typo in appendix 3

##Data Measurement
The data was organized by FiveThirtyEight (2024), collected form polls made by various institutions, they each use a distinct methodology. While FiveThirtyEight checks their methodology, and include the polling data if it meets their standard. An example of the methodology of one poll is included in [Appendix 1](#appendix1) It is a reliable and comprehensive source of US election polls， so we have choose this data set.

@@

```{r}
#| label: fig-samplesize
#| tbl-cap: Comparison of average polling result for two candiates
#| include: true
#| echo: false
#| warning: false
#| message: false

@@

# Appendix 1: Polling methodology {#Appendix1}

@@

## Sampling Approach
This survey employs Stratified Random Sampling, which involves divide the target population(In this case, the people who are eligible to vote in US) into subgroups(strata) based on their demographics characteristic[@stantchevaonline]. To simulate the national electorate, stratify the sample according to age, gender, race/ethnicity, education level, urban/rural domicile, and region. Also refer to the US Census data to determine the proportion of each strata, for example: if the census data shows there are 20% US citizen are between the age of 20 to 30, then there should be 20% of respondent in this age range. We aim for a starting sample of five thousand people since there were budget constraint.

## Respondent Recruitment
Partner with an online panel provider to find respondents that match each stratum’s specifications[@stantchevaonline]. Specify quotas to ensure that, for instance, you wish to have 18% of respondents from the Midwest or 25% aging between 30 - 40. Then randomly select respondent within each strata. To promote greater response rates and retention, provide a small monetary reward, such as $5 for each completed survey. To improve inclusivity and take into consideration differences in internet availability, use both phone and online surveys.

## Data Validation
To keep distinct replies between responses, make sure respondents don't participate more than once each wave, and highlight straight-lining, inconsistent replies, and other low-effort answers for data quality purposes[@horn1997effective].

@@

```{r}
#| label: fig-diagnostics_harris
#| tbl-cap: Model diagnostics for Harris model
#| include: true
#| echo: false
#| warning: false
#| message: false
par(mfrow = c(2, 2))  
plot(model_harris)
```

```{r}
#| label: fig-diagnostics_trump
#| tbl-cap: Model diagnostics for Trump model
#| include: true
#| echo: false
#| warning: false
#| message: false
par(mfrow = c(2, 2))  
plot(model_trump)
```
## Selection

>>>>

## Data Measurement
The data was organized by FiveThirtyEight (2024), collected form polls made by various institutions, they each use a distinct methodology. While FiveThirtyEight checks their methodology, and include the polling data if it meets their standard. An example of the methodology of one poll is included in [Appendix 1](#appendix1) It is a reliable and comprehensive source of US election polls， so we have choose this data set.

@@

```{r}
#| label: fig-samplesize
#| fig-cap: Sample Sizes of the Polls We Use
#| include: true
#| echo: false
#| warning: false
#| message: false

@@

# Appendix 1: Polling methodology {#appendix1}

@@

## Sampling Approach
This survey employs Stratified Random Sampling, which involves divide the target population(In this case, the people who are eligible to vote in US) into subgroups based on their demographics characteristic [@stantchevaonline]. To simulate the national electorate, stratify the sample according to age, gender, race/ethnicity, education level, urban/rural domicile, and region. Also refer to the US Census data to determine the proportion of each strata, for example: if the census data shows there are 20% US citizen are between the age of 20 to 30, then there should be 20% of respondent in this age range. We aim for a starting sample of five thousand people since there were budget constraint.

## Respondent Recruitment
Partner with an online panel provider to find respondents that match each stratum’s specifications [@stantchevaonline]. Specify quotas to ensure that, for instance, you wish to have 18% of respondents from the Midwest or 25% aging between 30 - 40. Then randomly select respondent within each strata. To promote greater response rates and retention, provide a small monetary reward, such as $5 for each completed survey. To improve inclusivity and take into consideration differences in internet availability, use both phone and online surveys.

## Data Validation
To keep distinct replies between responses, make sure respondents don't participate more than once each wave, and highlight straight-lining, inconsistent replies, and other low-effort answers for data quality purposes [@horn1997effective].

@@

```{r}
#| label: fig-diagnostics_harris
#| fig-cap: Model diagnostics for Harris model
#| include: true
#| echo: false
#| warning: false
#| message: false
#| fig.width: 10
#| fig.height: 7

par(mfrow = c(2, 2))  
plot(model_harris)
```

```{r}
#| label: fig-diagnostics_trump
#| fig-cap: Model diagnostics for Trump model
#| include: true
#| echo: false
#| warning: false
#| message: false
#| fig.width: 10
#| fig.height: 7

par(mfrow = c(2, 2))  
plot(model_trump)
```
## Selection
